Evaluating infectious disease forecasts \\ with allocation scoring rules

### 2024-02-22 alloscore_manuscript/alloscore-application-shorter.Rnw
merging first batch of elr edits

We arrive through this discussion at a three-step procedure for developing scoring rules for probabilistic forecasts:
\begin{enumerate}
  \item Specify a \emph{loss function} $s(x, y)$ that measures the loss associated with taking action $x$ when outcome $y$
    eventually occurs.
  \item Given a probabilistic forecast $F$, determine the \emph{Bayes act} $x^F$ that minimizes the expected loss under
    the distribution $F$.
  \item The \emph{scoring rule} for $F$ calculates the score as the loss incurred when the Bayes act was used: 
    $S(F, y) = s(x^F, y)$.
\end{enumerate}
This is a general procedure that may be applied in settings where it is possible to specify a quantitative loss
function. We call a scoring rule obtained from this procedure a \emph{Bayes scoring rule} --- a terminology we find to
be convenient but which is not, to our knowledge, standard.  In appendix \ref{sec:proper} we review the
basic fact from the scoring rule literature (e.g., \cite{dawid2007geometry,gneiting2007strictly}) that Bayes scoring
rules are proper by construction.

>>>>

We arrive through this discussion at a three-step procedure for developing scoring rules for probabilistic forecasts:
\begin{enumerate}
  \item Specify a \emph{loss function} $s(x, y)$ that measures the loss associated with taking action $x$ when outcome $y$
    eventually occurs.
  \item Given a probabilistic forecast $F$, determine the \emph{Bayes act} $x^F$ that minimizes the expected loss under
    the distribution $F$.
  \item The \emph{scoring rule} for $F$ calculates the score as the loss incurred when the Bayes act was used: 
    $S(F, y) = s(x^F, y)$.
\end{enumerate}
This is a general procedure that may be applied in settings where it is possible to specify a quantitative loss
function. We call a scoring rule obtained from this procedure a \emph{Bayes scoring rule} (noting that to our knowledge, this terminology is not standard).  In appendix \ref{sec:proper} we review the
result from the scoring rule literature (e.g., \cite{dawid2007geometry,gneiting2007strictly}) that Bayes scoring
rules are proper by construction.
